Characterizing the response of subarctic European vegetation to key environmental variables for land surface modeling of ozone pollution and risk assessment

### 2021-10-15 VegOzone.tex
Checked acknowledgements

\begin{acknowledgements}
  We thank NILU for performing the ozone measurements at Svanhovd for us, Bj{\o}rg Rognerud (Department of Geosciences, UiO) for processing SeNorge.no data with respect to beginning of growing season, Tore Flatlandsmo Berglen (NILU) for hourly pressure data from Svanhovd, NIBIO Environment Center Svanhovd for establishing and running the ozone garden both years, and Volkmar Timmermann (NIBIO) for sharing ICP Forest data from Svanhovd. This work was supported by the Research Council of Norway (Grant No. 268073).
\end{acknowledgements}

>>>>

\begin{acknowledgements}
  We thank NILU for performing the ozone measurements at Svanhovd for us, Bj{\o}rg Rognerud (Department of Geosciences, UiO) for processing SeNorge.no data with respect to the beginning of the growing season, Tore Flatlandsmo Berglen (NILU) for hourly pressure data from Svanhovd, NIBIO Environment Center Svanhovd for establishing and running the ozone garden both years, and Volkmar Timmermann (NIBIO) for sharing ICP Forest data from Svanhovd. This work was supported by the Research Council of Norway (Grant No. 268073).
\end{acknowledgements}
